% Meyers_Chris_Resume.tex

\documentclass[11pt, letterpaper]{article}

\input{Meyers_Chris_Settings}

\begin{document}

% =================================== Header ===================================
\input{Meyers_Chris_Header}

% ================================= Experience =================================
\subsection*{Experience}

\begin{itemize}
  \parskip=0.1em

% BEGIN Experience
  \item
  \headerrow
    % URL https://www.madwire.com
    {\textbf{Madwire}}
    {\textbf{Fort Collins, CO and Remote}}
  \\
  \headerrow
    {\emph{Staff Software Engineer}}
    {\emph{Apr. 2024 -- Present}}
  % SAME COMPANY
  \headerrow
    {\emph{Senior Software Engineer II}}
    {\emph{Sept. 2019 -- Apr. 2024}}
  % SAME COMPANY
  \headerrow
    {\emph{Software Engineer}}
    {\emph{Mar. 2019 -- Sept. 2019}}
  \begin{itemize*}
    \item[$\circ$] Leader of the foundation track that developed critical shared services including: credit escrow, public API gateway and token management, platform-wide activity stream, multi-transport notifications
    \item[$\circ$] Worked across teams and tracks to coordinate migrations and integrations with shared services
    \item[$\circ$] Provided guidance, mentorship, and technical direction to a team of software engineers
    \item[$\circ$] Introduced TypeScript project templates to provide a consistent and reliable developer experience
  \end{itemize*}
  % BLOCK END

\begin{comment} % Commented out on PDF, visible on website
  \item
  \headerrow
    % URL https://www.asrcfederal.com
    {\textbf{ASRC Federal Vistronix}}
    {\textbf{Fort Collins, CO}}
  \\
  \headerrow
    {\emph{Software Developer}}
    {\emph{Jan. 2019 -- Mar. 2019}}
  \begin{itemize*}
    \item[$\circ$] Worked on web applications in support of a USDA National Resource Conservation Service (NRCS) contract
  \end{itemize*}
  % BLOCK END
\end{comment}

  \item
  \headerrow
    % URL https://www.asrcfederal.com
    {\textbf{ASRC Federal Mission Solutions}}
    {\textbf{Moorestown, NJ}}
  \\
  \headerrow
    {\emph{Software Engineer, Display Systems}}
    {\emph{June 2018 -- Dec. 2018}}
  \begin{itemize*}
    \item[$\circ$] Worked on an R\&D project that experimented with map and graphics updates to the display system
    \item[$\circ$] Developed scripts that aided in converting the department build system to CMake which drastically reduced build times and improved build stability
  \end{itemize*}
  % BLOCK END

  \item
  \headerrow
    % URL https://mcgstrategic.com
    {\textbf{MCG Strategic}}
    {\textbf{Marlton, NJ}}
  \\
  \headerrow
    {\emph{Software Engineer}}
    {\emph{Feb. 2017 -- May 2018}}
  \begin{itemize*}
    \item[$\circ$] Lead backend developer and maintainer of client websites, web applications, and mobile apps
    \item[$\circ$] Contributed to the creation of engineering process best practices to strengthen development and QA workflow (deploying via Bitbucket webhooks, Bitbucket/JIRA integrations, Slack alerting)
    \item[$\circ$] Designed and developed internal automation tools that include a mobile app build/delivery system and a weekly time report generation system which saved several hours of manual work each week
  \end{itemize*}
  % BLOCK END

  \item
  \headerrow
    % URL https://www.asrcfederal.com
    {\textbf{ASRC Federal Mission Solutions}}
    {\textbf{Moorestown, NJ}}
  \\
  \headerrow
    {\emph{Software Engineer, Display Systems}}
    {\emph{Mar. 2015 -- Feb. 2017}}
  \begin{itemize*}
    \item[$\circ$] Designed, developed, and tested solutions in CMMI Level 5 for the U.S. Navy's real-time, mission critical Aegis Ballistic Missile Defense (BMD) system
    \item[$\circ$] Nominated as a mentor to help new employees adjust to their position
    \item[$\circ$] Lead developer of the display system for the Littoral Combat Ship's (LCS) SeaRAM weapon system
  \end{itemize*}
  % BLOCK END

\begin{comment} % Commented out on PDF, visible on website
  \item
  \headerrow
    % URL https://www.rowan.edu
    {\textbf{Rowan University}}
    {\textbf{Glassboro, NJ}}
  \\
  \headerrow
    {\emph{Web Developer, History Department}}
    {\emph{Nov. 2013 -- May 2015}}
  \begin{itemize*}
    \item[$\circ$] Updated and maintained the History Department's website
  \end{itemize*}
  % SAME COMPANY
  \headerrow
    {\emph{Network Assistant, Network \& System Services}}
    {\emph{July 2014 -- Sept. 2014}}
  \begin{itemize*}
    \item[$\circ$] Installed and maintained network infrastructure across the Glassboro campus
  \end{itemize*}
  % BLOCK END
\end{comment}
% END Experience

\end{itemize}

% ================================== Education =================================
\subsection*{Education}

\begin{itemize}
  \parskip=0.1em

% BEGIN Education
  \item
  \headerrow
    % URL https://www.rowan.edu
    {\textbf{Rowan University}}
    {\textbf{Glassboro, NJ}}
  \\
  \headerrow
    {\emph{Bachelor of Science, Computer Science}}
    {\emph{Sept. 2011 -- May 2015}}
  % BLOCK END
% END Education

\end{itemize}

% ============================== Technical Skills ==============================
\subsection*{Technical Skills}

\begin{itemize*}
% BEGIN TechnicalSkills
  \item Experience developing websites, web applications, and REST APIs using: % LANGUAGES web
  \begin{itemize*}
    \vspace{-0.2em}
    \item[$\circ$] JavaScript (TypeScript, Node.js, React), PHP, Go
    \vspace{-0.2em}
  \end{itemize*}
  \item Experience developing desktop and command-line interface (CLI) applications using: % LANGUAGES desktop
  \begin{itemize*}
    \vspace{-0.2em}
    \item[$\circ$] \CPP, Java, Python
    \vspace{-0.2em}
  \end{itemize*}
  \item Experience designing and managing relational databases (MySQL, PostgreSQL)
  \item Experience using Git, ClearCase, and Subversion version control systems
  \item Experience developing and deploying applications using Docker and Kubernetes (Skaffold, Helm)
  \item Experience designing and developing highly available distributed systems using RabbitMQ and Kafka
  \item Experience debugging software with visual debuggers and the command line GNU debugger (GDB)
  \item Experience as a member and leader of Agile teams utilizing Jira and Shortcut to manage tasks
% END TechnicalSkills
\end{itemize*}

\end{document}
